Deep Probabilistic Models for Camera Geo-Calibration

### 2018-08-13 chapters/introduction/introduction.tex
Ground-to-aerial geo-calibration

\subsection{Geo-Calibration}
\todo{add deterministic methods, add literature for time estimation}

@@

\subsection{Deep Learning in Geo-Calibration}
In recent years, deep neural networks (DNNs) were proven to be
extremely successful in many computer vision areas (\todo{citations}). 
The deep neural networks prove to be a good tool to extract high-level
image representations, this valuable ability offers great help for researchers
to conquer the problems like geo-localization and camera calibration.
Recent work on cross-view image
geo-localization~\cite{lin2013cross,lin2015learning,workman2015geocnn,workman2015wide}
has shown that convolutional neural networks are capable of extracting
features from geo-tagged aerial imagery that can be matched to features extracted
from the inquiry ground imagery.  Vo \etal~\cite{vo2016localizing} extend this
line of work, demonstrating improved geo-localization performance by
applying an auxiliary loss function to regress the ground-level camera
orientation with respect to the aerial image.

@@

\subsection{Ground-to-Aerial Geo-Calibration}
Data-driven scene matching approaches are widely used to localize a
query image by registering in a large dataset of geo-tagged images. 
Benefited from the fast growing monitoring satellite market, overhead
imagery grows fast nowadays, which also makes it a perfect source for
database of geo-tagged. We refer to the geo-calibration process of
matching the ground-level imagery to the aerial imagery as {\em
Ground-to-Aerial Geo-Calibration}.
%
Cross-view image pair is the basic element for ground-to-aerial
geo-calibration. It consists of a ground-level image and an overhead
image at the same location. In some cases, two images are also aligned
in orientation.

\todo{cite ground-to-aerial geo-calibration papers}

>>>>

\subsection{Geo-Calibration}
\todo{add deterministic methods}

@@

\subsection{Deep Learning in Geo-Calibration}
In recent years, deep neural networks (DNNs) were proven to be
extremely successful in many computer vision areas (\todo{citations}). 
The deep neural networks prove to be a good tool to extract high-level
image representations, this valuable ability offers great help for researchers
to conquer the problems like geo-localization and camera calibration.

@@

\subsection{Ground-to-Aerial Geo-Calibration}
Data-driven scene matching approaches are widely used to localize a
query image by registering in a large dataset of geo-tagged
images~\cite{im2gps, li2010location,zamir2010accurate}.
Benefited from the fast growing monitoring satellite and drone markets,
satellite/aerial imagery becomes more and more available than ever
before, which makes it a rich source for
reference database of geo-tagged images. We refer to the
geo-calibration methods which uses the aerial imagery as geographic
reference as {\em Ground-to-Aerial Geo-Calibration}.
%
Cross-view image pair is the basic element for ground-to-aerial
geo-calibration. It consists of a ground-level image and an overhead
image at the same location. In some cases, two images are also aligned
in orientation. 
%
Recent work on cross-view image
geo-localization~\cite{lin2013cross,lin2015learning,workman2015geocnn,workman2015wide}
has shown that convolutional neural networks are capable of extracting
features from geo-tagged aerial imagery that can be matched to features extracted
from the inquiry ground imagery.  Vo \etal~\cite{vo2016localizing} extend this
line of work, demonstrating improved geo-localization performance by
applying an auxiliary loss function to regress the ground-level camera
orientation with respect to the aerial image. Hu and Feng
\etal~\cite{mh2018cvm} achieve the state-of-the-art performance in
geo-localization by extracting cross-domain global features using
NetVLAD~\cite{arandjelovic2016netvlad} technique.
